### 2023-04-19 outputs/paper/paper.qmd
Updated pdf

# Model
```{r}
#| echo: false
#| warning: false
#| include: false

log_data <- read_csv(here::here("inputs/data/data.csv"))

#Reading in my model data 
log_model <- select(cad_data, Prov_Terr, Facility_Type)

# Recode Facility_Type to binary variable
log_model$Facility_Type <- ifelse(log_model$Facility_Type == "Private", 1, 0)

#Converting character variables to a factor 
log_model$Facility_Type <- factor(log_model$Facility_Type)
log_model$Prov_Terr <- factor(log_model$Prov_Terr)
head(log_model)
```

logit_model <- glm(
  Facility_Type ~ Prov_Terr, 
  data = log_model, 
  family = "binomial"
)
```

logit_model <- predictions(logit_model) |>
  as_tibble()

```{r}
#| echo: false
#| warning: false

logit_model |>
  ggplot(aes(
    x = Prov_Terr,
    y = estimate, 
    color = Facility_Type
  )) +
  geom_jitter(width = 0.01, height = 0.01, alpha = 0.3) +
  labs( 
    x = "Province",
    y = "Estimated Probability of School Type",
    color = "School Type"
  ) + 
  theme_classic() + 
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom")

>>>>

# Model
